Use and acquisition of causal relations for decision making under uncertainty using imperfect information games

### 2020-09-03 3rd_year_eval/Slides/3rd_year_slides.tex
ultimos detalles

\begin{frame}
\frametitle{Introduction: Relevance}
\begin{itemize}
\item Mainstream ideas in DMU work at the \textit{associative} level of information.
\item In fact, Optimal Policies in RL satisfy the classical (associative) criterion of Maximum Expected Utility \citep{webb2007game}.
\item Given the importance of Causation in science \textbf{we consider decision making theory that relies on causal information.}
\end{itemize}
\end{frame}

\subsection{Some Background}
\begin{frame}
\frametitle{Some Background}
\begin{itemize}
\item Rationality.
\item Decision Theory: rational decision making if and only if utility maximization
\item Causality: Interventions. Context and order.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{First Year}
\begin{itemize}
\item Using Equation \ref{first_version}, we devised a learning algorithm which assumed known the causal structure and learned both the parameters of the causal model of the environment, and an optimal action, yielding a performance similar to classic Reinforcement Learning algorithms which do not use causal information, but rather rely on the maximization of expected utility.
\item \cite{gonzalez2018playing} Presented as a poster at Causality Workshop ICML 2018 at Stockholm, Sweden.
\item Proposal Defense (27-Nov-2018).
\end{itemize}
\end{frame}

@@

\subsection{Causal-Structure Learning: A Random Graph Approach}{\label{random_graph}}
\begin{frame}
\frametitle{Causal-Structure Learning: A Random Graph Approach}
\begin{itemize}
\item Human beings focus on \textit{local} aspects while learning causal relations which are later unified into a single structure \citep{fernbach2009causal,waldmann2008causal, danks2014unifying}.
\item Following this idea, \cite{wellen2012learning} propose a model to explain how observations  and interventions are used by human beings to learn causal relations in terms of a local prediction-error learning.
\item We propose here a local probabilistic encoding of the uncertainty that a decision maker has over \textit{the existence or not of causal relations} between variables.
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Introduction: Relevance}
\begin{itemize}
\item Mainstream ideas in DMU work at the \textit{associative} level of information.
\item In fact, Optimal Policies in RL satisfy the classical (associative) criterion of Maximum Expected Utility \citep{webb2007game}.
\item Given the importance of Causation in science\footnote{\cite{lake2017building,pearl2018why}} \textbf{we consider decision making theory that relies on causal information.}
\end{itemize}
\end{frame}

\subsection{Some Background}
\begin{frame}
\frametitle{Some Background}
\begin{itemize}
\item Rationality.
\item Decision Theory: rational decision making if and only if expected utility maximization
\item Causality: Interventions. Context and order.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{First Year}
\begin{itemize}
\item Using Equation \ref{first_version}, we devised a learning algorithm which assumed known the causal structure and learned both the parameters of the causal model of the environment, and an optimal action, yielding a performance similar to classic Reinforcement Learning algorithms which do not use causal information, but rather rely on the maximization of expected utility based on associative information.
\item \cite{gonzalez2018playing} Presented as a poster at Causality Workshop ICML 2018 at Stockholm, Sweden.
\item Proposal Defense (27-Nov-2018).
\end{itemize}
\end{frame}

@@

\subsection{Causal-Structure Learning: A Random Graph Approach}{\label{random_graph}}
\begin{frame}
\frametitle{Causal-Structure Learning: A purely Bayesian + Random Graphs Approach}
\begin{itemize}
\item Human beings focus on \textit{local} aspects while learning causal relations which are later unified into a single structure \citep{fernbach2009causal,waldmann2008causal, danks2014unifying}.
\item Following this idea, \cite{wellen2012learning} propose a model to explain how observations  and interventions are used by human beings to learn causal relations in terms of a local prediction-error learning.
\item We propose here a local probabilistic encoding of the uncertainty that a decision maker has over \textit{the existence or not of causal relations} between variables.
\end{itemize}
\end{frame}
